Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
Placeholder for fractions
more todos
Abstract wrapping

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting companions,
though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker)
that delivers reliable (and often highly
multi-modal) posterior samplings for companion orbital parameters given sparse
radial-velocity data.
% Aims
Here we
perform a search for secondary companions of over 100,000 red-giant
stars observed in the
\apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined in a posterior sense, (2)~a
catalog of stars \nmultimodal\ stars that likely have companions, but for which
(in most cases) more observations would be needed to uniquely determine the
orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all \nstars\ stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

@@

>>>>

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting
companions, though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the
data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker) that
delivers reliable (and often highly multi-modal) posterior samplings for
companion orbital parameters given sparse radial-velocity data.
% Aims
Here we perform a search for secondary companions of \nstars\ red-giant stars
observed in the \apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined in a posterior sense, (2)~a
catalog of \nmultimodal\ stars that likely have companions, but for which
(in most cases) more observations would be needed to uniquely determine the
orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

\todo{To assess this, take boxes in log g-Teff}
We find that, empirically, XX\% of the subgiants and YY\% of the \RC\ stars have
companions with $XX < P < XX$~day.
\todo{Assuming selection function doesn't preferentially bias...}

@@

\todo{Expectation from theory? What's spectial at 10 days?}

\figurename~\ref{fig:todo} shows the orbital period and eccentricity...
